
```{r}
author = "D/ADC/0047"
```



```{r}
library(ggplot2)

```

# Import Data

```{r}
Titanic = read.csv("E:/First sem/rprogramming.RData/titanic.train.csv")

```

# Display first few rows

```{r}
head(Titanic,5)

```

# Calculate Summary Statistics

```{r}
summary(Titanic)

```

# Remove null values

```{r message=TRUE}
x = is.na(Titanic)
X = options(max.print = 100)
print(x)

```

# Identify and remove duplicates

```{r}
unique(Titanic)

```

# Create tables

# Frequency thable for 'survived' variable

```{r}
survival_freq <- table(Titanic$Survived)
print("Frequency table for Survived")

```

```{r}
print(survival_freq)
```
# create a barchart for 'survived' variable

```{r}
ggplot(Titanic, aes(x = Survived)) + geom_bar(color = "black",fill = "white",alpha = 0.7 ) 

```
# Create a barchart for 'sex' variable
```{r}
ggplot(Titanic, aes(x = Sex)) + geom_bar(color = "black",fill = "white",alpha = 0.7 ) 

```


# Frequency table for 'Pclass' variable

```{r}
class_freq <- table(Titanic$Pclass)
print("Frequency table for Pclass")
```

```{r}
print(class_freq)
```

# Frequency table for 'Sex' variable

```{r}
gender_freq <- table(Titanic$Sex)
print("Frequency table for Sex")
```

```{r}
print(gender_freq)
```

# Frequency table for 'Embarked' variable

```{r}
embarked_freq <- table(Titanic$Embarked)
print("Frequency table for Embarked")
```

```{r}
print(embarked_freq)
```


# Scatter plot

```{r}
ggplot(Titanic, aes(x = Age, y = Fare, color = factor(Survived))) +
  geom_point(size = 3, alpha = 0.8) +
  labs(title = "Scatterplot of Age vs Fare in Titanic Dataset (Colored by Survival)",
       x = "Age",
       y = "Fare",
       color = "Survived") +
  scale_color_manual(values = c("#FF0000", "#00FF00"), labels = c("No", "Yes"))

```
# Assuming you have the Titanic dataset loaded
```{r}

ggplot(Titanic, aes(x = Age)) +
  geom_histogram(binwidth = 5, fill = "skyblue", color = "black") +
  labs(title = "Histogram of Age in Titanic Dataset",
       x = "Age",
       y = "Frequency")

```
# Exploratory Data Analysis (EDA)

```{r}
set.seed(2)
df <- data.frame(Team = factor(rep(c("A", "B"), each = 200)),
                 Points = c(rnorm(200, mean = 15, sd = 3),
                            rnorm(200, mean = 12, sd = 4)))
ggplot(df, aes(x = Team, y = Points)) +
  stat_boxplot(geom = "errorbar", width = 0.5) +
  geom_boxplot(color = "red")
```


# Cross-Tabulation and Contingency Tables
```{r}
crs_tab = table(Titanic$Sex,Titanic$Survived)
```
```{r}
print(crs_tab)
```











